% 参考文献
\section*{参考文献}
\addcontentsline{toc}{section}{参考文献}

\begin{thebibliography}{99}

% VRP関連
\bibitem{vrp_classic}
Toth, P., \& Vigo, D. (2014).
\textit{Vehicle Routing: Problems, Methods, and Applications} (2nd ed.).
Society for Industrial and Applied Mathematics.

\bibitem{vrp_survey}
Braekers, K., Ramaekers, K., \& Van Nieuwenhuyse, I. (2016).
The vehicle routing problem: State of the art classification and review.
\textit{Computers \& Industrial Engineering}, 99, 300-313.

\bibitem{greedy_heuristics}
Golden, B. L., Raghavan, S., \& Wasil, E. A. (2008).
\textit{The Vehicle Routing Problem: Latest Advances and New Challenges}.
Springer Science \& Business Media.

% アルゴリズム関連
\bibitem{2opt}
Croes, G. A. (1958).
A method for solving traveling-salesman problems.
\textit{Operations Research}, 6(6), 791-812.

\bibitem{metaheuristics}
Gendreau, M., \& Potvin, J. Y. (2010).
\textit{Handbook of Metaheuristics} (Vol. 2).
Springer.

\bibitem{dijkstra}
Dijkstra, E. W. (1959).
A note on two problems in connexion with graphs.
\textit{Numerische Mathematik}, 1(1), 269-271.

% 資源回収・環境関連
\bibitem{waste_collection}
Beliën, J., De Boeck, L., \& Van Ackere, J. (2014).
Municipal solid waste collection and management problems: a literature review.
\textit{Transportation Science}, 48(1), 78-102.

\bibitem{green_logistics}
Erdoğan, S., \& Miller-Hooks, E. (2012).
A green vehicle routing problem.
\textit{Transportation Research Part E: Logistics and Transportation Review}, 48(1), 100-114.

\bibitem{ev_routing}
Schneider, M., Stenger, A., \& Goeke, D. (2014).
The electric vehicle-routing problem with time windows and recharging stations.
\textit{Transportation Science}, 48(4), 500-520.

% システム開発・実装関連
\bibitem{python_optimization}
Mitchell, S., O'Sullivan, M., \& Dunning, I. (2011).
PuLP: a linear programming toolkit for python.
\textit{The University of Auckland, Auckland, New Zealand}, 65.

\bibitem{networkx}
Hagberg, A., Swart, P., \& S Chult, D. (2008).
Exploring network structure, dynamics, and function using NetworkX.
\textit{Los Alamos National Lab.(LANL), Los Alamos, NM (United States)}.

\bibitem{streamlit}
Streamlit Inc. (2019).
Streamlit: The fastest way to build data apps.
Retrieved from https://streamlit.io/

\bibitem{folium}
Python Visualization Development Team. (2018).
Folium: Python Data, Leaflet.js Maps.
Retrieved from https://python-visualization.github.io/folium/

% 環境・CO2削減関連
\bibitem{co2_emissions}
環境省 (2021).
温室効果ガス排出量算定・報告・公表制度における算定方法・排出係数一覧.
Retrieved from https://ghg-santeikohyo.env.go.jp/

\bibitem{ev_impact}
Messagie, M., Boureima, F., Coosemans, T., Macharis, C., \& Van Mierlo, J. (2014).
A range-based vehicle life cycle assessment incorporating variability in the environmental assessment of different vehicle technologies and fuels.
\textit{Energies}, 7(3), 1467-1482.

% ユーザビリティ・HCI関連
\bibitem{usability}
Nielsen, J. (1994).
\textit{Usability Engineering}.
Morgan Kaufmann.

\bibitem{web_usability}
Krug, S. (2014).
\textit{Don't Make Me Think, Revisited: A Common Sense Approach to Web Usability} (3rd ed.).
New Riders.

% 日本国内の資源回収関連
\bibitem{japan_waste}
環境省 (2022).
一般廃棄物の排出及び処理状況等について.
Retrieved from https://www.env.go.jp/

\bibitem{japan_recycling}
一般社団法人プラスチック循環利用協会 (2022).
プラスチックリサイクルの基礎知識.
Retrieved from https://www.pwmi.or.jp/

% GIS・空間解析関連
\bibitem{gis_algorithms}
de Smith, M. J., Goodchild, M. F., \& Longley, P. (2007).
\textit{Geospatial Analysis: A Comprehensive Guide to Principles, Techniques and Software Tools}.
Troubador Publishing Ltd.

\bibitem{spatial_index}
Samet, H. (2006).
\textit{Foundations of Multidimensional and Metric Data Structures}.
Morgan Kaufmann.

% 最適化理論
\bibitem{optimization_theory}
Boyd, S., \& Vandenberghe, L. (2004).
\textit{Convex Optimization}.
Cambridge University Press.

\bibitem{combinatorial_optimization}
Papadimitriou, C. H., \& Steiglitz, K. (1998).
\textit{Combinatorial Optimization: Algorithms and Complexity}.
Courier Corporation.

% データ構造とアルゴリズム
\bibitem{algorithms}
Cormen, T. H., Leiserson, C. E., Rivest, R. L., \& Stein, C. (2009).
\textit{Introduction to Algorithms} (3rd ed.).
MIT Press.

% オペレーションズリサーチ
\bibitem{operations_research}
Hillier, F. S., \& Lieberman, G. J. (2015).
\textit{Introduction to Operations Research} (10th ed.).
McGraw-Hill Education.

% 関連するオープンソースソフトウェア
\bibitem{osm}
OpenStreetMap Contributors. (2023).
OpenStreetMap.
Retrieved from https://www.openstreetmap.org/

\bibitem{pandas}
McKinney, W. (2010).
Data structures for statistical computing in Python.
\textit{Proceedings of the 9th Python in Science Conference}, 445, 51-56.

\end{thebibliography}

\vspace{1em}
\noindent
\textbf{注記：} 本報告書で使用したオープンソースライブラリおよびツールの詳細については、
付録\ref{appendix:software}を参照のこと。
